\newpage

\Enabstract{
    The Radar Cross-Section (RCS) reduction using absorbing materials is one of the important measures to achieve radar stealth. Frequency selective surface (FSS), as a new type of structural absorbing material, plays an important role in RCS reduction. There are many structural parameters affecting the electromagnetic performance of FSS. How to effectively analyze the parameters of FSS absorbing structure and design the FSS structure to meet the specific target frequency band has become a hot topic of scholars. In this thesis, the structures analysis and intelligent optimization of FSS is presented, which is base on Microwave Intelligent Design Integration Studio (MIDIS).

    Task management, database system, and Bayesian optimization algorithm for MIDIS are programmed. The analysis of the passive single-ring FSS structure, the analysis of the active single-ring FSS structure, and the optimization the single-ring FSS absorbing structure are completed.

    The task management module centrally manages the computing tasks on the MIDIS platform by establishing a task queue. The implementation of the task management module reduces the time for creating tasks and improves the utilization efficiency of computing resources. According to the characteristics of FSS simulation data, a database system is designed. This database system can quickly store and query all simulation data, and provide a data interface for the design of other data analysis and optimization algorithm modules.

    Based on the database system, the passive FSS absorbing structure and the active FSS absorbing structure data processing module are completed. The variables of the single-ring FSS structure are traversed within a certain range. Through the process of database query, evaluation formula evaluation and data display, the structural parameters corresponding to the best performance of the structure are obtained. Through the dimension reduction technique, the influence of the variation between the structural variables on the absorbing performance is analyzed. The envelope of active FSS is processing by specifying the simulation variables corresponding to the active device, and the reflectivity curve corresponding to the active FSS structure is obtained. The simulation results for the active FSS absorbing structure do not match the measurement results. The problem is proposed by modifying the model and fitting the parasitic parameters of the device.

    This thesis also proposes an optimization algorithm based on model agent. The difference between the optimization algorithm and the evolutionary algorithm is that it creates a function distribution model by means of probability statistics, and finds the position of the optimal solution in the model. In order to compare the efficiency of the algorithm and the genetic algorithm, a single-ring FSS absorbing structure is designed, and the target frequency band is optimized to 4-8 GHz. The results show that both algorithms achieve the optimization goal, but the optimization time of the Bayesian optimization algorithm is shorter.

}
\Enkeywords{frequency selection surface, intelligent algorithm, database, absorbing material, Bayesian optimization algorithm}